\vspace{0.5em}
\noindent{\bf Ivan Ukhov} received the B.Sc. and M.Sc. degrees (hons.) in
computer science and computer engineering from St. Petersburg State
Polytechnical University, St. Petersburg, Russia, in 2008 and 2010,
respectively, and is currently pursuing the Ph.D. degree with the Department of
Computer and Information Science, Link\"{o}ping University, Link\"{o}ping,
Sweden, focusing on uncertainty quantification for electronic system design.

\vspace{0.5em}
\noindent{\bf Petru Eles} (M'99) is currently a Professor of embedded computer
systems with the Department of Computer and Information Science, Link\"{o}ping
University, Link\"{o}ping, Sweden. He has published a large number of technical
papers and several books in the area of embedded systems.

He received two best paper awards at the European Design Automation Conferences,
a best paper award at the Design Automation and Test in Europe Conference, and a
best paper award at the International Conference on Hardware/Software Codesign
and System Synthesis.

\vspace{0.5em}
\noindent{\bf Zebo Peng} (M'91--SM'02) is currently a Professor of computer
systems, the Director of the Embedded Systems Laboratory, and the Chairman of
the Division for Software and Systems with the Department of Computer Science,
Link\"{o}ping University, Link\"{o}ping, Sweden. He has published over 300
technical papers and four books in various topics related to embedded systems.

He has received four best paper awards and one best presentation award in major
international conferences.
