Let $\T: \outcomes \to \real$ be a \rv\ representing the lifetime of the considered system.
The lifetime is the time span until the system experiences a fault after which the system no longer meets the imposed requirements.
Let $\distribution_\T(\cdot | \pvw)$ be the distribution of $\T$ where $\pvw = (\pw_i)$ is a vector of parameters.
The survival function of the system is
\[
  \survival_\T(\t | \pvw) = 1 - \distribution_\T(\t | \pvw).
\]

The overall lifetime $\T$ is a function of the lifetimes of the processing elements, which are denoted by a set of \rvs\ $\{ \T_i \}_{i = 1}^\nprocs$.
Each $\T_i$ is characterized by a physical model of wear \cite{jedec} describing the fatigues that the corresponding processing element is exposed to.
Each $\T_i$ is also assigned an individual survival function $\survival_{\T_i}(\cdot | \pvw)$ describing the failures due to those fatigues.
The structure of $\survival_\T(\cdot | \pvw)$ with respect to $\{ \survival_{\T_i}(\cdot | \pvw) \}_{i = 1}^\nprocs$ is problem specific, and it can be especially diverse in the context of fault-tolerant systems.
$\survival_\T(\cdot | \pvw)$ is to be specified by the designer of the system, and it is assumed to be included in the specification $\specification$ (see \sref{problem-formulation}).
To give an example, suppose the failure of any of the $\nprocs$ processing elements makes the system fail, and $\{ \T_i \}_{i = 1}^\nprocs$ are conditionally independent given the parameters gathered in $\pvw$.
In this scenario,
\begin{equation} \elab{reliability-model}
  \T = \min_{i = 1}^\nprocs \T_i \hspace{1em} \text{and} \hspace{1em} \survival_\T(\t | \pvw) = \prod_{i = 1}^\nprocs \survival_{\T_i}(\t | \pvw).
\end{equation}

Our work in this context is motivated by the following two observations.
First, temperature is the driving force of the dominant failure mechanisms.
The most prominent examples include electromigration, time-dependent dielectric breakdown, stress migration, and thermal cycling \cite{xiang2010}; see \cite{jedec} for an exhaustive overview.
All of the aforementioned mechanisms have exponential dependencies on the operating temperature, which is taken into account by considering the parameters in $\pvw$ as adequate functions of temperature.
At the same time, temperature is tightly related to process parameters, such as the effective channel length and gate-oxide thickness, and can vary dramatically when those parameters deviate from their nominal values \cite{ukhov2014, juan2012}.
Meanwhile, the state-of-the-art techniques for reliability analysis of electronic systems lack a systematic treatment of process variation and, in particular, of the effect of process variation on temperature.

Second, having determined a probabilistic model $\survival_\T(\cdot | \pvw)$ of the considered system, the major portion of the associated computational time is ascribed to the evaluation of the parameterization $\pvw$ rather than to the model \perse, that is, when $\pvw$ is known.
For instance, $\pvw$ often contains estimates of the mean time to failure of each processing element given for a range of stress levels.
Therefore, $\pvw$ typically involves (computationally intensive) full-system simulations including power analysis paired with temperature analysis \cite{xiang2010}.

\begin{remark} \rlab{two-level-probabilistic-modeling}
It is important to realize that there are two levels of probabilistic modeling here.
First, the reliability model \perse\ is a probabilistic model describing the lifetime of the system.
Second, the parameterization $\pvw$ is another probabilistic model characterizing the impact of the uncertainty due to process variation on the reliability model.
Consequently, the overall model can be thought of as a probability distribution over probability distributions.
Given an outcome of the fabrication process, that is, $\pvw$, the lifetime remains random.
\end{remark}
